Forecasting biodiversity in breeding birds using best practices

### 2017-09-19 manuscript/draft.Rmd
Fix title page

---
title: "Best practices for forecasting changes in biodiversity: an example using breeding birds"
author:
- David J. Harris
- Shawn D. Taylor
- Ethan P. White
bibliography: refs.bib
csl: csl.csl
geometry: left=3.5cm, right=3.5cm, top=2.25cm, bottom=2.25cm, headheight=12pt, letterpaper
fontsize: 12pt
header-includes:
    - \usepackage{times}
    - \usepackage{setspace}
    - \usepackage{booktabs}
    - \doublespacing
    - \usepackage{lineno}
    - \linenumbers
output:
  pdf_document: default
  html_document: default
---

@@

>>>>

---
title: "Forecasting biodiversity in breeding birds using best practices"
author:
- David J. Harris$^1$ (corresponding author)
- Shawn D. Taylor$^2$
- Ethan P. White$^1$
bibliography: refs.bib
csl: csl.csl
geometry: left=3.5cm, right=3.5cm, top=2.25cm, bottom=2.25cm, headheight=12pt, letterpaper
fontsize: 12pt
header-includes:
    - \usepackage{times}
    - \usepackage{setspace}
    - \usepackage{booktabs}
    - \doublespacing
    - \usepackage{lineno}
    - \linenumbers
output:
  pdf_document: 
    keep_tex: true
  html_document: default
---

$^1$ Department of Wildlife Ecology and Conservation, University of Florida, Gainesville, FL, United States

$^2$ School of Natural Resources and Environment, University of Florida Gainesville, FL, United States

@@

\newpage
